%-----------EXPERIENCE-----------%
\vspace{-10pt}
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
    { ClearEstate }{ July 2024 -- Present }
    { Full Stack Software Engineer }{ Toronto, Ontario }
    \begin{itemize}
    \resumeItem{ Develop and enhance features for ClearEstate's estate settlement platform using Laravel PHP and Vue.js for user-friendly solutions. }
    \resumeItem{ Maintain and optimize the codebase, ensuring high performance, scalability, and reliability through regular code reviews. }
    \resumeItem{ Collaborate with cross-functional teams to implement functionalities that streamline estate management and enhance user experience. }
    \resumeItem{ Utilize Git and Jira to coordinate development efforts and ensure timely delivery of project milestones. }
    \end{itemize}
    \resumeSubheading
    { Cactus App }{ September 2023 -- April 2025 }
    { Co-Founder and Lead Developer }{ Kingston, Ontario }
    \begin{itemize}
    \resumeItem{ Co-founded a cross-platform loyalty rewards app, architecting a complete ecosystem with customer and business applications (React Native, Laravel PHP, Vue.js, PostgreSQL). }
    \resumeItem{ Led full-stack development of a production-ready platform, implementing features like QR code point collection, rewards management, and CI/CD pipelines using GitHub Actions. }
    \resumeItem{ Successfully exited the company for \$20,000 after 19 months, showcasing strong product-market fit and technical execution. }
    \end{itemize}
    \resumeSubheading
    { Ecobee }{ April 2022 -- May 2023 }
    { Machine Learning and Data Engineering Intern }{ Toronto, Ontario }
    \begin{itemize}
    \resumeItem{ Maintained production services in the Ecobee ecosystem, including ETL jobs (Apache Beam) and ML pipelines (Kubeflow). }
    \resumeItem{ Engineered an end-to-end evaluation pipeline for a computer vision model, optimizing performance and accuracy. }
    \resumeItem{ Implemented a Kubeflow pipeline for smoke/CO alarm detection, enhancing deployment and system reliability. }
    \resumeItem{ Developed a custom metrics API to monitor services, ensuring adherence to SLOs and enabling proactive issue resolution. }
    \end{itemize}
\resumeSubHeadingListEnd